Almost compatible functions and infinite length games

### 2015-12-02 articles/almost-compatible-functions-and-topological-games/article.tex
finish kurepa family argument

  \begin{proof}
    We use the family \(\mc K\) of all compact
    open sets in the constructed topology on
    \(\omega_n\) as our witness. Of course, every Lindel\"of set in
    a locally countable space is countable, and the closure of every
    countable set is a compact countable set; thus \(\mc K\)
    is cofinal in \([\omega_n]^\omega\).
    It is Kurepa since for every countable set \(A\), there are only
    countably many distinct compact open sets in \(\cl A\): TODO finish
  \end{proof}

>>>>

  \begin{proof}
    We use the family \(\mc K\) of all compact
    open sets in the constructed topology on
    \(\omega_n\) as our witness. Of course, every Lindel\"of set in
    a locally countable space is countable, and the closure of every
    countable set is a compact countable set; thus \(\mc K\)
    is cofinal in \([\omega_n]^\omega\).
    It is Kurepa since every countable set is contained in a countable
    compact open subspace of \(\omega_n\); this subspace has a countable
    base of compact open sets, which closed under finite unions enumerates
    all compact open subsets of the subspace.
  \end{proof}
